A quantitative framework for investigating the reliability of empirical network construction

### 2018-11-27 manuscript/reply_to_reviewers.tex

		\textbf{R:} We agree that it is dangerous to suggest that anyone sample less, that is why we have not done so. We argue only that the amount of sampling required to be confident that co-occurring species do not interact is large -- likely beyond what is feasible for speciose systems given the limited resources available to many researchers. Sampling across most network studies is almost certainly not sufficient, but data which would allow readers to judge this (i.e., number of times each species is observed, independent of numbers of observed interactions) is not generally provided. We chose to be more charitable than the Reviewer and assume that those compiling empirical networks are sampling as much as possible given the constraints of their system and available resources. Infinite sampling would, of course, be the best option but it is unlikely that researchers will be able to perpetually increase sampling.

@@

		\textbf{R:} The redundant line has been removed. Thank you for pointing this out.

	10. Unsure about the point of filtering networks [[done]]

		\begin{refquote}
		Line 295 to 302.  I would think that this second step (i.e., filtered networks) is to explore sampling not to determine how networks will be influenced by uncertainty?  Do you need the filtering step to evaluate uncertainty (as written it seems that this is the case)?
		\end{refquote}

		\textbf{R:} The filtering was intended to show how uncertainty likely warps our current understanding of network properties like connectance. If we do not observe 20-50\% of the interactions in a network, then many network properties in the published literature will be inaccurate. Even worse, networks compiled under different levels of uncertainty (e.g., species with more or less variable traits, or studies with multiple sampling methods or only one) or with different sampling efforts will have network structure metrics that are inaccurate to different degrees. Filtering networks in the way that we do could give an idea of how many networks are missing, but we do not think it is necessary to evaluate uncertainty (we believe that examining the posterior distributions directly is a better approach there). We have rephrased these lines (XX-XX) to emphasize that the filtered networks are intended to demonstrate the consequences of uncertainty more than anything else.

		\begin{quotation}
			Measures of network structure which are based on empirical networks that are missing interactions may differ substantially from the values that would be obtained if detection certainty and variation in interactions over space and time could be removed. To demonstrate this, we created a suite of filtered networks for each posterior network. 
		\end{quotation}

@@

		\textbf{R:} We have cited addition literature as recommended by Reviewer 1, including a paper by Jordano. If the Reviewer has any suggestions of specific papers that they feel are missing, we would be happy to consider them as well. Note, however, that we do not intend our manuscript to be a complete review of the literature surrounding interaction probabilities. We hope that the citations we have added appear more balanced to the Reviewer.

	3. Comment on weighted metrics [[done]]

		\begin{refquote}
		L36ff The authors should note the value of weighted metrics in taking account of sampling biases.
		\end{refquote}

		\textbf{R:} We do not see how weighted metrics (which we infer mean metrics including interaction strength/frequencies based on the Reviewer's comment below) account for sampling biases. It seems to us that measures of interaction strength should be \emph{more} susceptible to sampling biases, not less, as abundant species are both more likely to have their interactions recorded and more likely to have these interactions recorded as strong/frequent. We have rephrased the introduction so that the original line 36 no longer appears. If the Reviewer strongly feels that weighted metrics somehow do sampling biases, we must ask for clarification as to why. We are willing to add a note as requested, but only if we are convinced that weighted metrics are indeed useful in this regard.

@@

	4. Demand for extension to weighted networks [[not done]]

		\begin{refquote}
		L45 It is a shame not to give some idea of how the method could be extended (or is this the intention of the authors?). For empirical analysis of networks it is rare to use binary networks given the value of weighted networks for taking account of sampling biases. Indeed, I am much less concerned about whether an interaction never occurs, and much more concerned with the frequency of occurrence.
		\end{refquote}

		\textbf{R:} As stated above, we do not agree that weighted networks reduce sampling biases. Moreover, we disagree that it is rare to use binary networks as most food webs (for example) are still binary. It takes an even greater sampling effort to quantify interaction strengths than the presence and absence of links, so for species-rich systems in particular there simply are not many high-quality weighted networks published. If the Reviewer is only concerned about weighted interactions, we congratulate them on their tractable study system. Nevertheless, we do not wish to exclude the many researchers who are not so fortunate.
		\smallskip
		To model frequencies of interactions, ...
			 [[Do we want to add a bit of non-binary stuff or just make it clearer that we are talking about feasibility and that probabilities of occurrance could be layered on later?]]

@@

		\textbf{R:}

	6. Process uncertainty poorly defined. [[done]]

		\begin{refquote}
		L76ff ‘Process uncertainty’ is not defined. The simplistic example of interaction uncertainty (fish eating a cactus) does not help the reader understand the detail of what is meant by ‘interaction uncertainty’. The two examples of ‘local constraints’ (weather and habitat) are operating on completely different temporal scales (note – it is defined differently in L109). I would regard the issue of weather as much closer to detection uncertainty (e.g. for a pollinator, it would be likely to be interacting if the weather was better), whereas the issue of habitat is closer to the authors’ ‘interaction uncertainty’ (the species don’t interact because they are not, or never, co-occurring in a habitat). Also if the species occur in different habitats then with an appropriate spatial scale of sampling then they do not co-occur – so the issue seems redundant. [[I suspect that the authors are thinking of a meta- or master network in much of their study, but this is not clear (or I have misunderstood and it needs to be explained better), i.e. the predicted presence of an interaction is not the presence of an interaction at the local site (taking detection and process uncertainty into account) but the ability to assess ‘interaction uncertainty’.]][[This is a bit separate from their issue]]
		\end{refquote}

		\textbf{R:} As our manuscript is not concerned with partitioning sources of uncertainty, we felt it was unproductive to get bogged down in a debate over the precise definitions of process vs. interaction uncertainty and which external influences might contribute to which sources (there is enough overlap that simple statements such as "bad weather increases process uncertainty" are, at best, incomplete). To remove this problem, we have rephrased the introduction and discussion to refer to the questions of whether two species \emph{can} interact under ideal conditions and whether they \emph{do} interact at a given site and time. We hope that this reframing, and the addition of clear statements that our framework is not intended to separate different sources of uncertainty, will remove the Reviewer's confusion.
		\smallskip
		Our mention of habitat as a factor affecting the probability of species interacting at a site was not intended to refer to species using different habitats, but rather the possibility that habitat type might affect interaction probabilities. For example, a more open patch of forest might have different interaction probabilities than a denser patch even if the same set of species use both patches. Of course the Reviewer is correct that habitat also affects which species are present at a site. We include co-occurrence in process uncertainty since co-occurrence does not tell us much about whether an interaction is feasible under ideal conditions (which would certainly include co-occurrence). This speaks to our point above that external factors (habitat, weather, etc.) can affect multiple levels of uncertainty at once. In fact, habitat also likely affects detection uncertainty since it is often harder to observe interactions in dense vegetation. So, in short, separating sources of uncertainty based on the external factors which contribute to them is not a particularly useful endeavour.

	7. Point about temporal scales of interaction [[done]]

@@

		\begin{refquote}
		L76ff Different interactions occur at different temporal scales, so it is important to consider where the role of this study lies. For instance, a pollinator-flower interaction is quick (and even the evidence of it, e.g. pollen on the insect, is not long-lasting) whereas an active gall-former interaction could be present for a couple of months and could be detected for even longer (on senescing leaves).
		\end{refquote}

		\textbf{R:} Long-term interactions may be easier to detect, but we do not see how this affects process uncertainty. Spatial variation in interaction probabilities will affect all interaction types, as does variation in abundances between years, so we cannot conceive of any interactions that are exempt from this issue. The timescale of an interaction (and the evidence it leaves) does affect detection uncertainty, so we have added a note in that section. Long-term interactions may fail to be detected, however, and we now add an example to make it clear that detection uncertainty applies to even long-term interactions such as gall-forming (indeed, our results suggest that uncertainty in gall-forming is quite high).

@@

			\end{quotation}

	8. Confusion about goal of modelling [[not done]]

		\begin{refquote}
		I was struggling to really understand what the authors were really trying to model (partly because of the lack of a link between the theoretical and empirical parts of the paper). Are the authors trying to estimate L (the probability that an interaction is feasible or not – I would describe this as a ‘master’ or meta- network), or is it that they are trying to estimate X|L (the probability that the interaction locally occurs)? I would be interested in both, but the second aspect seemed to be ignored in the gall-former example.
		\end{refquote}

		\textbf{R:} In the case study, we are modelling L (the probability that an interaction is feasible). We do not have quantitative data within sites in our dataset, so we cannot isolate the probability of detecting an interaction at a site from the probability that the interaction occurs. This is also the probability we were most interested in. We do note, however, that one could also model X|L using the same framework if there were independent counts of co-occurrences and interactions within a single site.

@@

		\textbf{R:}

	16. Filtering seems arbitrary [[done]]

		\begin{refquote}
		L298 These seem arbitrary. It is not clear what is filtered, or its justification – is it the unique interactions, unique interaction per site or samples? How do these compare to typical sampling effort?
		\end{refquote}

		\textbf{R:} We have rephrased lines XX-XX to make it clearer that the filtered networks are intended to demonstrate how network structure changes as uncertainty increases (and we miss more interactions). As stated, we filtered networks created using the posterior distributions. There are therefore no sites or samples in question here. We are simply retaining a random 90\%-10\% of the interactions (or removing a random 10\%-90\%; these are equivalent) of the interactions in the "true" (posterior) network. We hope that this rephrasing is clearer.

			\begin{quotation}
				Measures of network structure which are based on empirical networks that are missing interactions may differ substantially from the values that would be obtained if detection certainty and variation in interactions over space and time could be removed. To demonstrate this, we created a suite of filtered networks for each posterior network. Taking a posterior network as the "true" network, we randomly sampled 90\%, 80\%, 70\%, 60\%, 50\%, 40\%, 30\%, 20\%, and 10\% of the interactions to create a new "filtered" network.
			\end{quotation}

		Note that our model is not concerned with partitioning different sources of variation; the filtering levels we present therefore represent uncertainty from all sources. As such, comparing them directly to "typical sampling effort" would be an apples-to-oranges comparison. We do note that~\citet{Weinstein2017a} found a detectability of 23.3\% for interactions despite high sampling effort,~\citet{Jordano2016} found that about half of unobserved interactions did not qualify as "forbidden links", and~\citet{Bartomeus2013} found that 59\% of interactions were detected. We therefore do not think that the range of filtering levels we applied were particularly unreasonable (although we note that none of the above studies refer to plant-galler networks). That said, the Reviewer is correct that the values we chose were absolutely arbitrary. To make this clear, we now filter in 10\% increments from 90\% to 10\% to illustrate a broader range of uncertainty.

@@

	17. Expand discussion of results on line 321 [[not done]]

		\begin{refquote}
		L321 This is a really important and interesting set of results that are worthy of greater discussion. The issue of metrics from sampled networks is important, but gets lost in the paper. Please expand upon this.
		\end{refquote}

		\textbf{R:} [[This is the network metrics bit - need to expand in discussion.]]
